Bending magnet RAy Tracing using (Bx, By, Bz) vs (x, y, z).
This element is a companion to the commandline program {\tt abrat}.
It integrates through a 3-D field map for a bending magnet, including
coordinate transformations.
No synchrotron radiation calculations are included at this time.

{\bf Coordinates}

The coordinates of the field map are right-handed system (x, y, z), where z is along the length of the magnet, x is 
to the right as viewed along the direction of beam propagation, and y is up.
The user must specify the (x, z) coordinates of three points:
\begin{itemize}
\item Nominal entrance point: \verb|XENTRY| and \verb|ZENTRY|. These give the coordinates of reference trajectory at
  the exit of the previous element. In the limit of a hard-edge model, this would be at the entrance to the magnetic field 
  region.
\item Vertex point: \verb|XVERTEX| and \verb|ZVERTEX|. These give the coordinates of vertex point, which is the intersection
  of the reference lines from the entrance and exit.
\item Nominal exit point: \verb|XEXIT| and \verb|ZEXIT|. These give the coordinates of reference trajectory at
  the exit of the previous element. In the limit of a hard-edge model, this would be at the exit from the magnetic field 
  region.
\end{itemize}
The bending angle is equal to the angle between two lines: the line from \verb|ENTRY| to \verb|VERTEX| and the
line from \verb|VERTEX| to \verb|EXIT|.
The \verb|L| and \verb|ANGLE| parameters supplied by the user are used for geometry calculations (e.g., floor coordinates) only.

The \verb|DXMAP|, \verb|DZMAP|, \verb|YAWMAP|, and \verb|FSE| values can be used to optimize the field map to ensure that
the horizontal reference trajectory is not displaced at the exit of the element.
The optimization feature of the \verb|abrat| program can be used to determine these values.

{\bf Matrix generation}

{\tt elegant} will use tracking to determine the transport matrix for \verb|BRAT| elements, which 
is needed for computation of twiss parameters and other operations.
This can require some time, so {\tt elegant} will cache the matrices and re-use them for
identical elements.

{\bf Integration methods}

The original (and default) integration method is Bulirsch-Stoer integration of the Lorentz force equation.
As an alternative, one can use the faster, rotation-based method of the \verb|FTABLE| element.
For repeated use, the two methods should be compared and a choice made based on the user's needs.
