This element simulates a time-dependent kicker magnet as a rectangular
dipole with no fringe field effects.  To use this element, you must
supply an SDDS file giving the time-dependent waveform.  The element
is called {\tt BUMPER} to because {\tt HKICK}, {\tt VKICK}, {\tt
KICKER} are used for steering magnets.

The arrival time of the beam is taken to define the reference time,
$t=0$.  Hence, if the waveform file has the maximum amplitude at
$t=0$, the beam will get kicked at the peak of the waveform.  If the waveform
peaks at $t=t_{peak}$, then setting \verb|TIME_OFFSET| equal to $-t_{peak}$
will ensure that the beam is kicked at the peak amplitude.

By default, the kicker fires on the first beam passage.  However, if 
\verb|FIRE_ON_PASS| is used, then the kicker is treated like a drift space until
the specified pass.

If \verb|PHASE_REFERENCE| is non-zero, then the initial timing is
taken from the first time-dependent element that has the same
\verb|PHASE_REFERENCE| value.  This would allow, for example,
simulating several kickers firing at the same time.  Delays relative
to this reference time can then be given with positive adjustments to
\verb|TIME_OFFSET|.

The waveform input file need not have equispaced points in time.  However, the
time values should increase monotonically.

The deflection map, if provided, should have four floating-point columns
\begin{enumerate}
\item Transverse coordinates \verb|x| and \verb|y|, with units of \verb|m|.
\item Kick multipliers \verb|xpFactor| and \verb|ypFactor|, which are dimensionless quantities.
\end{enumerate}
The resulting kick in each plane for a particle with coordinates $(x, y, t, \delta)$ is 
\begin{equation}
\Delta q^\prime (x, y, t, \delta) = \frac{\theta A(t) f_q(x, y)}{1 + \delta},
\end{equation}
where $q$ stands for $x$ or $y$, $\theta$ is the specfied deflection angle, 
$A(t)$ is the time-dependent amplitude waveform, and $f_q(x, y)$ is the
deflection map factor for the $q$ plane at the particle's location.

The data in the deflection map file must be sorted so that \verb|x| changes fastest, which can be accomplished using
the command
\begin{verbatim}
sddssort input.sdds -column=y,incr -column=x,incr 
\end{verbatim}

This element simulates a dipole kicker only.  For multipole kickers, see the
{\tt MBUMPER} element.