This element simulates a set of beam-driven dipole modes in a cavity using the fundamental theorem of beam loading and phasor rotation.
It is similar to {\tt TRFMODE}, but it allows faster simulation of more than
one mode.  Also, the mode data is specified in an SDDS file.  This file can be
generated using the APS version of URMEL, or by hand. It must have the following
columns and units:
\begin{enumerate}
\item {\tt Frequency} --- The frequency of the mode in Hz.  Floating point.
\item {\tt Q} --- The quality factor.  Floating point.
\item {\tt ShuntImpedance} or {\tt ShuntImpedanceSymm} --- The shunt
  impedance in Ohms/m, defined as $V^2/(2*P)/x$ or $V^2/(2*P)/y$ (i.e., ``circuit definition'').
  Floating point. By default, {\tt ShuntImpedance} is used.  However,
  if the parameter \verb|USE_SYMM_DATA| is non-zero, then {\tt
  ShuntImpedanceSymm} is used.  The latter is the full-cavity shunt
  impedance that URMEL computes by assuming that the input cavity used
  is one half of a symmetric cavity.
\end{enumerate}

The file may also have the following columns:
\begin{enumerate}
\item {\tt beta} --- Normalized load impedance (dimensionless).  Floating point. If not given, the
 $\beta=0$ is assumed for all modes. 
\item {\tt xMode} --- If given, then only modes for which the value is nonzero will produce an
 x-plane kick.  Integer.  If not given, all modes affect the x plane.
\item {\tt yMode} --- If given, then only modes for which the value is nonzero will produce an
 y-plane kick.  Integer.  If not given, all modes affect the y plane.
\end{enumerate}
    
In many simulations, a transient effect may occur when using this
element because, in the context of the simulation, the impedance is
switched on instantaneously.  This can give a false indication of the
threshold for instability. The {\tt RAMP\_PASSES} parameter should
be used to prevent this by slowly ramping the impedance to full
strength.  This idea is from M. Blaskiewicz (BNL).

Normally, the field dumped in the cavity by one particle affects trailing particles in the same turn.
However, if one is also using a \verb|TRWAKE| or \verb|ZTRANSVSE| element to simulate the short-range wake of the cavity, this would be double-counting.
In that case, one can use \verb|LONG_RANGE_ONLY=1| to suppress the same-turn effects of the \verb|RFMODE| element.
